\documentclass[11pt, oneside]{report}   	
%\usepackage{geometry}                		
  		
\usepackage{graphicx}		
\usepackage{amssymb}
\usepackage{listings}
%SetFonts

\title{Report of MI2.01 Systems \& Networks\\
\vskip 2cm
Centralized Chat System}
\author{Loc Thi Thuy Linh}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

\section*{1. Problem}
Implementing a centralized chat system, similar to Internet Relay Chat (IRC). In such a system, client-to-client text messages must first be passed to a centralized server, then the server forwards the messages to the destination client.
\\
In detail, the system should work with multiplexed, nonblocking TCP socket.
\begin{itemize}
 \item \textbf{Sever side} 
 	\begin{itemize}
	\item Listening on a specific port.
	\item Receive data and forward data to another clients.
	\item Server serves each new client with a separated fork().
	\item Main process and the forked processes use pipe() as communication mechanism.
	\end{itemize}
\item \textbf{Client side:} 
 	\begin{itemize}
	\item Takes the server hostname from STDIN or from program arguments.
	\item Connects to the server.
	\item Waits for input message from STDIN
	\item Sends them as messages to server and prints incoming messages (from other clients, forwarded by the server) on the client?s terminal.
	\item Client should separate a thread for input and a thread for networking
	\end{itemize}
\end{itemize}

\section*{2. Deploy the program}
\begin{itemize}
\item 
\item 

\item 

\end{itemize}

\end{document}  